Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
done with first final version !!

Representing a scene using a reduced set of representatives, with adapted similarity strategies allows us to improve ASSR performance compared to the BOF approaches based on GMMs. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- are represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates.

@@

This assertion shall be studied further in future work by considering data-driven convolutional networks, larger databases and more diverse applications, such as pleasantness prediction \cite{lafaySoundscapePilot, lafayPartI} as well as other tasks in ecoacoustics.

>>>>

Representing a scene using a reduced set of representatives, with adapted similarity strategies allows us to improve ASSR performance compared to the BOF approaches based on GMMs which have been demonstrated to be equivalent to early integrations scheme on well balanced datasets \cite{lagrange:hal-01082501}. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- are represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates.

@@

Those outcomes shall be studied further in future work by considering larger databases and more diverse applications, such as pleasantness prediction \cite{lafaySoundscapePilot, lafayPartI} as well as emerging tasks in ecoacoustics.
